% Sommerville  - Glossary
% Smith  - Requirements  - Reference Material
% Smith  - Requirements  - Specific System Description  - Problem Description  - Terminology and Definitions
% Hewitt  - Infrastructure Design  - Standards and guidelines and conventions
% Hewitt  -  Acronyms and Symbols
\newsectionnobreak{Conventions for Report Writing}{sec:conv}
The project has strict standards in respect of conventions even in reports
that contain no code, ultimately to support the `write once, use many times' concept,
so that text may be cut, edited and pasted into source code, or indeed used safely to define
variable names, constraints on their values and physical dimensions.
Thus, since many compilers support only ASCII characters, only ASCII is allowed
in reports. Similarly, very long lines (typically arising from MS Windows wordprocessing)
should be split at the ends of sentences, and preferably so that maximum line length
is $120$~characters. A number of tools are available in \T{tex/importools}.
Contributors may use their style of choice for both reports (and code) provided
they follow systems that allow for automatic conversion to the conventions
expected in the \nep \ repositories, and are prepared to help construct gitlab runners and
github hooks to this end. However, it will be generally found easier to use \LaTeX \ and
bibtex as indicated below.

For shorter documents it is acceptable to use Markdown in the `dialect' defined by
\F{PANDOC}, see Annex~A of~\cite{y3re314}. Resulting .md files frequently convert
straightforwardly to \LaTeX \ format, using the md2tex.bash script from \T{tex/importools}.


\subsection{General textual issues}\label{sec:REF_text}
It is helpful to use \LaTeX \ newcommand for certain keywords where they have a special
format or because the terminology is not fully established. Although some do not, most
people do find variations in use of spelling, punctuation, capitalisation etc.\ to be irritating,
and so the following conventions will be enforced where possible: 
\begin{itemize}
\item use of \LaTeX \ newcommand for , viz. \verb-\-papp \ and  \verb-\-exc \ instead of explicit
proxyapp or mini-app and \exc \  respectively
\item punctuation, viz.\ eg.\verb-\- rather than e.g.
\item hyphenation, generally to be avoided because \LaTeX \ may use it to break lines, viz.\ finite element rather than finite-element (or simply FE), opensource rather than open source, major exception is abbreviation of dimensions (below).
\item capitalisation, eg.\ Exascale rather than exascale
\item abbreviation of dimensions, 2-D and 3-D preferred to 2D and 3D or 2d and 3d
\item spelling, UK English preferred, and  '-ise' etc.\ preferred to '-ize'
\item no spaces between authors' initials in bibtex files (see also \Sec{REF_citations})
\item consistent usage of acronyms, employing the table of \Sec{acro}
\item consistent usage of mathematical symbols, employing the table of \Sec{symbol}
\end{itemize}

\subsection{Citations}\label{sec:REF_citations}
Regarding citations, those for unpublished reports MUST include a link to a
website, such as arXiv, and it would be helpful if links to other open-access
material were also given.
Use of the following conventions for constructing the keys of citations should help avoid clashes:
\begin{enumerate}
\item For published papers, use where possible an $8$-character alphanumeric for published papers,
consisting of the first two letters of the first author's name, the last two digits
of the year in the Gregorian calendar, and the first $4$~letters of the first \emph{significant}
word (ie.\ not `The' or~`On') of the title, preserving capitalisations.
Thus the paper~\cite{Ba13What} by Bangerth and Heister, published in 2013 and
entitled `What makes computational open source software libraries successful?',
has key~`Ba13What'.
\item Books and theses should be keyed with the full second-name(s) of the author(s) strung together
without capitalisation, up to a limit of approx.~$30$ characters, using `etal'
to indicate any omitted author-names. As an example, the book by Rouson, Xia
and~Xu~\cite{rousonxiaxu} has key~`rousonxiaxu'.
\item If there are duplicates in different files, then preface
each key with the name of the .bib file it is in, for other duplicates within a file,
add `2', `3' etc.\ to the end of the key.
\end{enumerate}

\subsection{Software Compatibility}\label{sec:REF_compat}
\input{REF/conv}

\clearpage
\newsection{Acronyms}{sec:acro}
\input{REF/acro}

\clearpage
\newsection{Symbols}{sec:symbol}
\input{REF/symb}
