
How to configure git

Option to add personal profile

Email address for support neptune@ukaea.uk

List of projects/packages

Quick links

Separate the subject from body with a blank line and limit the subject line to 50 characterss

Importance of Slack

producing FMS reports collaboratively using git and mostly LaTeX some markdown,
markdown is not a standard, except very minimally, so I would demand compatibility with pandoc.

Zenodo indexing for s/w

How to Contribute

Community Code of Conduct see charter.tex
to include  Acknowledging and Citing

``Write code for people, not computers".
Literate programming. Interleaving documentation and codebase - minimises risk of code and documentation getting out of sync.
Use of Doxygen

C++ Core Guidelines (Bjarne Stroustrup, Herb Sutter)
\url{https://github.com/isocpp/CppCoreGuidelines/blob/master/CppCoreGuidelines.md}
Rules for high-performance or low-latency applications (otherwise Stroustrop's tour is 
reasonably comprehensive, includes chapters on numerics and
concurrency (parallelism)~\cite[\S\S\,14,15]{stroustroptour}
Mainly ``Don't optimize prematurely, but design to enable later optimization when it seems
it might be appropriate". Note that
Communication across nodes is \exc bottleneck at the Exascale.

Rouson~et~al's $12$~rules
\begin{enumerate}
\item Write code that comments itself.
\item Name all constants.
\item Make constants constant.
\item Minimize global data.
\item Make global data constant.
\item Provide global type parameters, including precision specifiers.
\item Provide global conditional debugging.
\item Declare intent for all procedure arguments.
\item Avoid side effects when possible, particularly in a function.
\item Make all derived type components private.
\item Indent loops and procedure/module executable statements.
\item Prevent implicit typing globally.
\end{enumerate}

Notes on DPC++ in ../ts/notes\_on\_dpc++.md
