% Hewitt  - Use Cases
% Sommerville  - User requirements definition
% Smith  - Problem Statement
% Smith  - Requirements  - Introduction
% Smith  - Requirements  - Requirements  - Functional Requirements
% Smith  - Requirements  - General System Description  - User Characteristics

The largest input to the process, representing UKAEA Tokamak Science
Department appears under Technical Specification~\Sec{TS}, so that it may
be accompanied by a detailed response. Instead, there is presented an appreciation
of the properties of the plasma edge in \Sec{props}.

The Departmental input, although it deals with other aspects of the specification,
focusses more on the physical processes to be modelled and the approaches likely to
be required. The following \Sec{RB2} records interactions with UKAEA Engineers, although
a subsequent meeting clarified that the main demand for \nep\ at that time was that it be a
modular, component-based design, equally suitable for integration into ANSYS OptisLang$^{TM}$
as VECMAtk (with more detailed requirements likely to follow when the software became more developed).
Thereafter the  next \Sec{use_case}  contains use cases, followed by \Sec{general-remarks}
describing general requirements deducible from the use cases.

\newsection{Physical properties of the edge plasma}{sec:props}
\input{RB/edgeprop}

\newsection{Engineering Requirements Baseline}{sec:RB2}
\input{RB/engineers_requirements}

\newsection{Use Cases}{sec:use_case}
\input{RB/use_case_physicist}
\input{RB/use_case_engineer}
\input{RB/use_case_particle_specialist}
\input{RB/use_case_FEM_background}

\newsection{General Remarks}{sec:general-remarks}
Particular, important general aspects of the use cases and \Sec{TS} requirements may be
as follows.
Calculations may need be (re)started, perhaps from databases of calculations as envisaged by the 
IMAS development.  Someone from the experimental side might want to specify input parameters
by duplicating those of a particular say JET 
shot at a given time, using an database of experimental results.
Physicists of either stamp (theoretical or experimental) will likely want compatibility with
analysis software such as OMFIT~\cite{omfitwebsite} and tools to speed publication in
the scientific literature of results obtained.
An engineer may simply want to ``change surface A to another design and repeat calculation".

Generally, minimising the number of new languages and systems people have to learn, especially
in view of the need to attract people to the project and community, seems a good idea, so that
a Domain Specific Language (DSL) should for
example be based on one or more language(s) that are already well-known to many technical people,
such as Julia, Python or \LaTeX.
Equally \nep \ software cannot be allowed to ossify, so the suggestion 
is everywhere to have a preferred option and an allowed option where this makes sense.
