\subsection{Use Cases: Particle Specialists}\label{sec:use-cases-particle-specialists}

\emph{As a particle specialist I:}

\begin{itemize}
\item am very familiar with particle based methods.
\item may not be familiar with FEM implementation details but have a working
  understanding of the approach.
\item may not be familiar with low level languages.
\item may not be familiar with HPC hardware and architectures.
\item understand how to describe complex physical processes such as
  radiation, recombination, ionisation, charge exchange using both
  particle and FEM data.
\item may not have applied UQ techniques before but may have an
  understanding of distributions/ensembles from statistical mechanics.
\end{itemize}

\emph{I want to:}

\begin{itemize}
\item describe particle based operations both collectively and per particle,
  eg.\ :
\begin{itemize}
\item creation and deletion of particles potentially from complex
  distributions.
\item computation with particle data - per particle and collectively.
\item identification of groups of particles.
\item representation of arbitrary per particle data.
\end{itemize}
\item visualise particle and FEM data - snapshots and trajectories.
\item create new finite element functions on appropriate function spaces.
\item add source/sink terms to governing equations (solved with FEM).
\item define particle source and sink regions using the simulation domain
  geometry.
\item define regions of interest, eg.\ surfaces, as part of diagnostics.
\item identify particles near surfaces/points/volumes of interest.
\item create and use global data structures for computation,
  eg.\ diagnostics.
\item represent particle data as FE functions:

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \item through pointwise projection.
  \item line integration over particle trajectory.
  \end{enumerate}
\item use non-trivial functions in my loops, eg.\ erfc, gamma.
\item define functions using expansion coefficients, eg.\ ionisation rate
  function approximated by an exponential expansion.
\item evaluate these functions using both particle and FEM data.
\item describe pairwise operations that implement physical processes.
\item describe and sample from non-trivial statistical distributions.
\item perform simulations in a reproducible manner.
\end{itemize}

\emph{So that I can:}

\begin{itemize}
\item use particles as a kinetic description for plasma and neutrals.
\item represent highly-collisional regimes by fluid approximations.
\item describe plasma-neutral and plasma-plasma interactions.
\item use abstractions/DSLs to write once, run anywhere as much as possible.
\item experiment with models quickly and efficiently.
\item perform ensemble computations and averages.
\item perform UQ and verification.
\end{itemize}
