\subsection{Use Cases: Engineers}\label{sec:use-cases-engineers}

\emph{As a thermomechanical engineer I:}

\begin{itemize}
\item work with a large range of open source and proprietary codes which
  requires bindings to other tools, eg\.:

  \begin{itemize}
  \item FMU
  \item Python (Jupyter and regular)
  \item OptiSLang
  \item Twinbuilder
  \end{itemize}
\item work with CAD software to generate geometries which I want to
  propagate through my workflow.
\item am interested in heat fluxes in all forms: from time and space
  averages to high resolution 3D time and data.
\item need to be able iterate on designs quickly and in an automated way.
\item am neither an HPC expert nor a plasma / tokamak physicist.
\end{itemize}

\emph{and I want to:}

\begin{itemize}
\item know, given a sensible physics model provided by other experts, what
  the transient peak and average heat loads are on plasma facing
  components.
\item not have to understand software dependencies and be able to install and
  run easily eg.\ ``in the cloud''.
\item be able to configure the software to undertake parameter scans.
\item have a handle on the sensitivity of the solution to the inputs and
  sources of error / uncertainty.
\item be able to re-use the spatio-temporal heat fluxes as a model in more
  thermo-mechanical calculations. This means:

  \begin{itemize}
  \item reading in the solution after the calculation.
  \item using a fit to the data in the form of eg.\ a reduced order model of
    the heat fluxes, surrogates etc.
  \item being able to export CAD geometries and import solutions back into
    engineering tools eg.\ ANSYS.
  \end{itemize}
\item have reproducible workflows to save and share with colleagues
  (eg.\ databases of inputs / outputs / config).
\item export results flexibly to inter-operate with multiple surrogate
  frameworks.
\item be in the loop with development process so it is possible to keep other
  workflows up to date.
\end{itemize}

\emph{This would mean I can:}

\begin{itemize}
\item design components with colleagues within eg.\ STEP.
\item make use of the \nep\ software in combination with proprietary tools that engineers
  know inside out.
\item be insulated, to a sensible extent, from the complexities of the
  numerics, plasma physics and HPC.
\end{itemize}
